Revision of MS #2018:11:32569:0:0:REVIEW

### 2019-02-09 docs/reviews.Rmd
Modified line numbers referenced in response to reviewrs

- *We chose to keep the word "major" in L26 to maintain consistency with the authors' original wording, but we have included quotations to denote this.*

- *In L142 (Now L145) We now say that "ex situ parameters can result in erroneous weight estimates"*

- *Ass suggested, we have changed "major" from L175 to "key" (now L201).*

@@

*The text now correctly states the research was performed in the Bahamas (L38).*

>>>>

- *We chose to keep the word "major" in L26 (now L30) to maintain consistency with the authors' original wording, but we have included quotations to denote this.*

- *In L142 (Now L150) We now say that "ex situ parameters can result in erroneous weight estimates"*

- *Ass suggested, we have changed "major" from L175 to "key" (now L206).*

@@

*The text now correctly states the research was performed in the Bahamas (L37).*
